\texttt{davos}: The Python package smuggler

### 2022-09-30 paper/main.tex
add some more relevant keywords
rough version of software functionalities section

\begin{keyword}
Python \sep Jupyter Notebook \sep Google Colaboratory \sep Reproducibility \sep Package management \sep Pip install
\end{keyword}

@@

\subsection{Software functionalities}\label{sec:functionalities}

\subsection{The \texttt{smuggle} statement}

\subsection{The onion comment}

\subsection{The \texttt{davos} config}

\subsection{Additional functionality}

>>>>

\begin{keyword}
Reproducibility \sep Open science \sep Python \sep Jupyter Notebook \sep Google Colaboratory \sep Package management
\end{keyword}

@@

\subsection{Software functionalities}%\label{sec:functionalities}

\subsubsection{The \texttt{smuggle} statement}
Importing \texttt{davos}\comment{in a Jupyter notebook} enables an additional Python keyword: ``\texttt{smuggle}".
The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
If a smuggled package does not exist in the local environment, \texttt{davos} will install it, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.

\subsubsection{The onion comment}
For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}. An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed. Onion comments follow a simple syntax based on the ``type comment" syntax introduced in PEP 484 \cite{vanREtal14} and are designed to make managing packages via \texttt{davos} intuitive and familiar. To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{snippets/snippet1.pdf}
\caption{\small \textbf{Figure 1}}
\label{fig:snippet1}
\end{figure}

%\definecolor{backgroundgrey}{RGB}{244,246,249}
%\definecolor{commentgrey}{RGB}{91,99,110}
%\definecolor{keywordred}{RGB}{194,11,36}
%
%\lstset{
%    backgroundcolor=\color{backgroundgrey},
%    basicstyle=\footnotesize\fontfamily{qag}\selectfont, %\ttfamily,
%    breaklines=true,
%    commentstyle=\color{commentgrey},
%    language=Python,
%    emph={import, smuggle, from, as},
%    emphstyle=\color{keywordred},
%}
%
%\begin{lstlisting}
%import davos
%
%# if numpy is not installed locally, pip-install it and display verbose output
%smuggle numpy as np    # pip: numpy --verbose
%
%# pip-install pandas without using or writing to the package cache
%smuggle pandas as pd    # pip: pandas --no-cache-dir
%
%# install scipy from a relative local path, in editable mode
%from scipy.stats smuggle ttest_ind # pip: -e ../../pkgs/scipy
%\end{lstlisting}

\subsubsection{The \texttt{davos} config}

\subsubsection{Additional functionality}
